---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# script-me-a-river

<!-- badges: start -->
<!-- badges: end -->

The goal of script-me-a-river is to ...

# Setup a new user

Open your `.Rprofile` with:

```{r}
usethis::edit_r_profile()
```

Add to `.Rprofile`:

```{r}
Sys.setenv(CKAN_URL="https://data.dpaw.wa.gov.au")
Sys.setenv(CKAN_API_KEY = "your CKAN API key")
```

# Data flow

* Two xslx spreadsheets come from monitoring surveys per river each week.
* Place those four xslx into `/data` and run `sonde_to_biosys.Rmd`.
* With data now appended to BioSys datasets X and Y (TODO create), run `swan_surfer.Rmd`.
* Outputs (figures as PDF, reports as HTML) are uploaded to CKAN datasets:
  * https://data.dpaw.wa.gov.au/dataset/water-quality-monitoring-swan-canning-estuary-2019
  * https://data.dpaw.wa.gov.au/dataset/water-quality-monitoring-swan-canning-catchment-2019
* PICA can hot-link PDF figures from data catalogue.